### 2015-03-02 paper_50_sdlc-ae.tex
added some database diagrams single space the references
adding some SDLC-AE diagrams

In order for an SDO to properly track the elements of CRI, a data storage system should be available to store the appropriate data.  A consistent storage system should help to avoid the problem of inaccurate
data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
is implemented correctly by allowing limited changes to existing data, it will be able to alliviate
some of the dishonesty that is currently present in software projects \cite{Rost2011}. This storage system will be named the SDLC Analytic Engine (SDLC-AE). Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.

@@

\begin{figure}[ht]
\includegraphics[scale=.7]{images/sdlc-ae.png}
\caption{SDLC ANALYTIC ENGINE}
\label{fig:sdlc-ae}
\end{figure}

@@

       \begin{figure}[ht]
            \centering
            \includegraphics[scale=.55]{images/raw_tables.png}
            \caption{TABLES FOR RAW CRI DATA}
            \label{fig:raw}
        \end{figure}%

@@

@@

>>>>

In order for an SDO to properly track the elements of CRI, a data storage system should be available to store the appropriate data.  A consistent storage system should help to avoid the problem of inaccurate
data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
is implemented correctly by allowing limited changes to existing data, it will be able to alleviate
some of the dishonesty that is currently present in software projects \cite{Rost2011}. This storage system will be named the SDLC Analytic Engine (SDLC-AE). Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.

@@

\begin{figure}[ht]
\includegraphics[scale=.6]{images/sdlcae.png}
\caption{SDLC ANALYTIC ENGINE}
\label{fig:sdlc-ae}
\end{figure}

@@

       \begin{figure}[ht]
            \centering
            \includegraphics[scale=.55]{images/raw_tables.png}
            \caption{TABLES FOR RAW CRI DATA}
            \label{fig:raw}
        \end{figure}

@@

       \begin{figure}[ht]
            \centering
            \includegraphics[scale=.55]{images/score_tables.png}
            \caption{TABLES FOR INTERMEDIATE CRI SCORES}
            \label{fig:score_tables}
        \end{figure}%

@@

       \begin{figure}[ht]
            \centering
            \includegraphics[scale=.55]{images/final_score_tables.png}
            \caption{TABLES FOR FINAL CRI SCORES}
            \label{fig:final_score_tables}
        \end{figure}
